---
title: "Examples of {openairmaps} Functionality"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE,
  warning = FALSE,
  out.width = "100%"
)
```

This vignette outlines some core functionality in `{openairmaps}`. For further examples, please see the [online book](https://bookdown.org/david_carslaw/openair/).

```{r setup}
library(openairmaps)
```

# Access UK Monitoring Data with Lat/Lng Information

`openair::importUKAQ()` has the `meta` argument which appends the latitude and longitude of each site to the returned data. If not using data from `importUKAQ()`, ensure that your data has coordinate data appended in a similar way.

```{r read}
london_data <-
  openair::importUKAQ(site = c("my1", "hors", "cll2"),
                      year = 2020,
                      meta = TRUE)

london_data

names(london_data)
```

To find sites to import data from, you can visualise UK monitoring networks using `networkMap()`. Alternatively, `searchNetwork()` will allow you to target a specific region.

```{r network}
networkMap(source = c("aurn", "aqe"),
           year = 2020,
           control = "variable")
```

# Polar Plot Maps

The `polarMap()` family includes `polarMap()`, `annulusMap()`, `freqMap()`, `percentileMap()`, `windroseMap()`, `pollroseMap()`, and `diffMap()`, and all work similarly to create interactive air quality maps:

```{r polar}
polarMap(london_data,
         c("no2", "pm10"), 
         popup = c("site", "site_type"),
         label = "site")
```

By setting `static` to `TRUE` you will receive a static version of the map, which may be more useful for academic articles.

```{r polarstatic}
polarMap(london_data,
         c("no2", "pm10"),
         static = TRUE,
         d.icon = 100)
```

# Trajectory Maps

`trajMap()` has almost identical arguments to `openair::trajPlot()`, and likewise `trajLevelMap()` with `openair::trajLevel()`.

```{r trajmap}
trajMap(traj_data, colour = "pm10")
```

```{r trajlevel}
trajLevelMap(traj_data)
```
